The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-06 paper2_JNLS/paper.tex
NM

Introduce waves. \\
Introduce papers: PRF, PNAS, and J Stat Phys. \\

>>>>

Though once dismissed as sailor's tales, rogue waves are now recognized as a real and present threat to naval structures (cite). These abnormally large waves are inherently tied to emergence of non-Gaussian statistics in the sea surface.

%Introduce waves. \\
Introduce papers: PRF, PNAS, and J Stat Phys. \\
